
\subsubsection{Hybrid resilience for MPI + tasks codes}
\label{Cappello-MPI-Tasks-Resilience} % add label, replace xx with your initials

% start new section for referencing, please use the name of your bibfile here instead of report2015 (.bib)
\begin{refsection}[collab_report_FC_MPI_task_resilience]

\paragraph{Participants}

\begin{itemize*}
 \item Omer Subasi, BSC, Ph. D. Student 
 \item Tatiana Martsinkevich, Inria, Ph. D. Student 
 \item Franck Cappello, ANL, Senior Computer Scientist
 \item Osman Unsal, BSC, Senior Researcher 
 \end{itemize*}

\paragraph{Research topic and goals}~\\

We investigate fault-tolerant protocols, mitigating transient errors, that can be applied to task-parallel message-passing applications. 
Our approach limits the consequences of a fault to the task that experienced it and allows a fast and asynchronous recovery that is more efficient than the
conventional full-application rollback-recovery. The proposed protocol will implemented in Nanos; a dataflow runtime for the task-based OmpSs programming model; and the PMPI profiling layer to fully support hybrid OmpSs+MPI applications.
The OmpSs+MPI programming model provides several advantages over conventional programming models in terms of performance and the potential for using asynchronous fault tolerance. 

\paragraph{Results for current year}~\\

This collaboration started in summer 2014.  In our experiments we demonstrate that our fault tolerant solution has a reasonable overhead, with a maximum observed overhead of 4.5\%. We also show that fine-grained parallelization is important for hiding the overheads related to the protocol as well as the recovery of tasks.

The collaboration has been implemented by the 3 months visit of  Tatiana Martsinkevich to BSC during the summer of  2014.
Since then a paper has been written and is under submission ~\cite{Martsinkevich-Cluster2015}.  

\paragraph{Visits and meetings}

\begin{itemize*}
 \item Tatiana Martsinkevich (Inria) to BSC from June 2014 to October, 2014.
\end{itemize*}


\paragraph{Impact and publications}~\\

A paper is under submission ~\cite{Martsinkevich-Cluster2015}.  
% print list of publications containing the ``own'' keyword (for publications done within this project and year)
\printbibliography[heading=none,keyword=own]

Further impact
\begin{itemize*}
    \item none yet
% \item impact there
\end{itemize*}

\paragraph{Person-Month efforts}~\\

\begin{itemize*}
 \item Tatiana Martsinkevich (Inria): 6 PM
 \item Omer Subasi (BSC): 4 PM 
 \item Osman Unsal (BSC): 0.5 PM 
 \item Franck Cappello (ANL): 1 PM 
\end{itemize*}

\paragraph{Future plans}~\\

After the two visits planned from July 2015, we plan to work on a join-paper, submit if to IPDPS, PPoPP or CCGRID and then present the results during the November JLESC workshop.

\paragraph{References}~\\

Provide a few bibliographical references here.

% print list of publications not from this project but of other relevance
\printbibliography[heading=none,notkeyword=own]

\end{refsection}
